Import_MCData

### 2024-03-06 Code/Import_MCData.Rmd
Put data.table back in. I don't think it is redundant
New file path to Culture Catalog

library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(photobiologyWavebands)

@@

CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))

>>>>

library(tidyverse)
library(lubridate)
library(broom)
library(data.table)
library(zoo)
library(photobiologyWavebands)

@@

CultureCatalog <- readRDS(file = file.path("..", "Data",  "RawData","CultureCatalog.Rds"))
